---
title: "Handedness_Step1_3_2ACC"
output:
  word_document: default
  pdf_document: default
---
```{r}
library(readr)
library(psych)
library(tidyr)
library(nlme)
library(multcomp)
library(ggpubr)
library(ggplot2)
library(lme4)
library(lsmeans)
library(afex)
library(dplyr)
```
descriptive stats
```{r}
#Logfile <- read_csv("~/Desktop/Handedness/Data_new/Step1/SLR_GestureType_prior.csv")
Logfile <- read_csv("~/Desktop/Handedness/Data_new/Step1/SLR_GestureType.csv")

View(Logfile)
str(Logfile)
summary(Logfile)
```
```{r}

Logfile$subject <- as.factor(Logfile$subject)
str(Logfile)
# define between and within subjects variables

# define between and within subjects variables
Logfile$handedness <- factor(Logfile$handedness,
                                            levels = c(0,1),
                                            labels = c("Lefty","Righty"))

Logfile$Lat2 <- factor(Logfile$Lat2,
                                            levels = c(0,1),
                                            labels = c("Lefty","Righty"))

Logfile$Strength <- factor(Logfile$Strength,
                                            levels = c(0,1),
                                            labels = c("Mixed","Extreme"))

Logfile$sex <- factor(Logfile$sex,
                                            levels = c(0,1),
                                            labels = c("Female","Male"))

Logfile$version <- factor(Logfile$version,
                                         levels = c(1,2),
                                         labels = c("Response with Left Finger","Response with Right Finger"))



Logfile$SLR <- factor(Logfile$SLR,
                                          levels = c(0,1),
                                          labels = c("Left Hands","Right Hands"))


#Logfile$GestureType <- factor(Logfile$GestureType,
                                #         levels = c(0,1),
                                 #       labels = c("Palm","Pointer"))

Logfile$Strategy <- factor(Logfile$Strategy,
                                          levels = c(0,1,2),
                                          labels = c("Mental Rotation","Thumb Strategy","Both"))


#final check the data 
str(Logfile)
View(Logfile)
# Get descriptives
Means.Table<-describe(Logfile)

Means.Table #call the object to see the means table

#use knitr function to call the object to see the means table.
knitr::kable(Means.Table, digits = 2, caption = 'Mixed Means Table')

```


** descriptive analysis **

```{r}
Left_Finger <- filter(Logfile, version == "Response with Left Finger")
psych::describe(Left_Finger$ACC)

Left_Finger_LH <- filter(Left_Finger, SLR == "Left Hands")
psych::describe(Left_Finger_LH$ACC)

Left_Finger_RH <- filter(Left_Finger, SLR == "Right Hands")
psych::describe(Left_Finger_RH$ACC)

Right_Finger <- filter(Logfile, version == "Response with Right Finger")
psych::describe(Right_Finger$ACC)
```


```{r}
eRHR <- filter(Logfile, Lat2 == "Righty",
               Strength == "Extreme")
psych::describe(eRHR$ACC)


eRHR_R <- filter(eRHR, SLR == "Right Hands")
psych::describe(eRHR_R$ACC)

# eRHR_PA <- filter(eRHR, GestureType == "Palm")
# psych::describe(eRHR_PA$ACC)
# 
# eRHR_Po <- filter(eRHR, GestureType == "Pointer")
# psych::describe(eRHR_Po$ACC)

```

```{r}
eLHR <- filter(Logfile, Lat2 == "Lefty",
               Strength == "Extreme")
psych::describe(eLHR$ACC)

eLHR_R <- filter(eLHR, SLR == "Right Hands")
psych::describe(eLHR_R$ACC)

# eLHR_pa <- filter(eLHR, GestureType == "Palm")
# psych::describe(eLHR_pa$ACC)


```

```{r}
mRHR_L <- filter(Logfile, Lat2 == "Righty",
               Strength == "Mixed",
               SLR == "Left Hands")
psych::describe(mRHR_L$ACC)
psych::describe(mRHR_L$RT)


mRHR_R <- filter(Logfile, Lat2 == "Righty",
               Strength == "Mixed",
               SLR == "Right Hands")
psych::describe(mRHR_R$ACC)
psych::describe(mRHR_R$RT)


```

```{r}
mHR_Left_Finger <- filter(Logfile, Strength == "Mixed",
                          version == "Response with Left Finger")

mHR_Left_Finger_LH <- filter(mHR_Left_Finger, SLR == "Left Hands")
psych::describe(mHR_Left_Finger_LH$ACC)

mHR_Left_Finger_RH <- filter(mHR_Left_Finger, SLR == "Right Hands")
psych::describe(mHR_Left_Finger_RH$ACC)

```


```{r}
# mHR_Po <- filter(Logfile, Strength == "Mixed",
#            GestureType == "Pointer")
# mHR_Po_R <- filter(mHR_Po, SLR == "Right Hands")
# psych::describe(mHR_Po_R$RT)
# 
# mHR_Po_L <- filter(mHR_Po, SLR == "Left Hands")
# psych::describe(mHR_Po_L$RT)

```

```{r}
mLHR_R <- filter(Logfile, Lat2 == "Lefty",
               Strength == "Mixed",
               SLR == "Right Hands")
psych::describe(mLHR_R$ACC)

```

```{r}
# Pa <- filter(Logfile, GestureType == "Palm")
# 
# Pa_RHR <- filter(Pa, Lat2 == "Righty")
# psych::describe(Pa_RHR$ACC)
# 
# Pa_eRHR <- filter(Pa_RHR, Strength == "Extreme")
# psych::describe(Pa_eRHR$ACC)
# 
# Pa_eRHR_RH <- filter(Pa_eRHR, SLR == "Right Hands")
# psych::describe(Pa_eRHR_RH$ACC)
# 
# Pa_eRHR_LH <- filter(Pa_eRHR, SLR == "Left Hands")
# psych::describe(Pa_eRHR_LH$ACC)
# 
# Pa_mRHR <- filter(Pa_RHR, Strength == "Mixed")
# psych::describe(Pa_mRHR$ACC)
# 
# Pa_mRHR_RH <- filter(Pa_mRHR, SLR == "Right Hands")
# psych::describe(Pa_mRHR_RH$ACC)
# 
# Pa_mRHR_LH <- filter(Pa_mRHR, SLR == "Left Hands")
# psych::describe(Pa_mRHR_LH$ACC)
# 
# Pa_LHR <- filter(Pa, Lat2 == "Lefty")
# psych::describe(Pa_LHR$ACC)
# 
# Pa_eLHR <- filter(Pa_LHR, Strength == "Extreme")
# psych::describe(Pa_eLHR$ACC)
# 
# Pa_eLHR_RH <- filter(Pa_eLHR, SLR == "Right Hands")
# psych::describe(Pa_eLHR_RH$ACC)
# 
# Pa_eLHR_LH <- filter(Pa_eLHR, SLR == "Left Hands")
# psych::describe(Pa_eLHR_LH$ACC)
# 
# Pa_mLHR <- filter(Pa_LHR, Strength == "Mixed")
# psych::describe(Pa_mLHR$ACC)
# 
# Pa_mLHR_RH <- filter(Pa_mLHR, SLR == "Right Hands")
# psych::describe(Pa_mLHR_RH$ACC)
# 
# Pa_mLHR_LH <- filter(Pa_mLHR, SLR == "Left Hands")
# psych::describe(Pa_mLHR_LH$ACC)

```

```{r}
# Pa_mLHR_RH_Right_Finger <- filter(Pa_mLHR_RH, version == "Response with Right Finger")
# psych::describe(Pa_mLHR_RH_Right_Finger$RT)
# 
# Pa_mLHR_LH_Right_Finger <- filter(Pa_mLHR_LH, version == "Response with Right Finger")
# psych::describe(Pa_mLHR_LH_Right_Finger$RT)
# 
# Pa_eLHR_RH_Right_Finger <- filter(Pa_eLHR_RH, version == "Response with Right Finger")
# psych::describe(Pa_eLHR_RH_Right_Finger$RT)
# 
# Pa_eLHR_LH_Right_Finger <- filter(Pa_eLHR_LH, version == "Response with Right Finger")
# psych::describe(Pa_eLHR_LH_Right_Finger$RT)
# 
# Pa_eRHR_RH_Right_Finger <- filter(Pa_eRHR_RH, version == "Response with Right Finger")
# psych::describe(Pa_eRHR_RH_Right_Finger$RT)
# 
# Pa_eRHR_LH_Right_Finger <- filter(Pa_eRHR_LH, version == "Response with Right Finger")
# psych::describe(Pa_eRHR_LH_Right_Finger$RT)

```


```{r}
# Pa_L_Finger <- filter(Pa, version == "Response with Left Finger")
# psych::describe(Pa_L_Finger$ACC)
# 
# Pa_L_Finger_RH <- filter(Pa_L_Finger, SLR == "Right Hands")
# psych::describe(Pa_L_Finger_RH$ACC)
# 
# 
# Pa_L_Finger_LH <- filter(Pa_L_Finger, SLR == "Left Hands")
# psych::describe(Pa_L_Finger_LH$ACC)
# 
# 
# Pa_R_Finger <- filter(Pa, version == "Response with Right Finger")
# 
# Pa_R_Finger_RH <- filter(Pa_R_Finger, SLR == "Right Hands")
# psych::describe(Pa_R_Finger_RH$ACC)
# 
# 
# 
# Pa_R_Finger_LH <- filter(Pa_R_Finger, SLR == "Left Hands")
# psych::describe(Pa_R_Finger_LH$ACC)


```


```{r}
# Po <- filter(Logfile, GestureType == "Pointer")
# 
# Po_RHR <- filter(Po, Lat2 == "Righty")
# psych::describe(Po_RHR$ACC)
# 
# Po_eRHR <- filter(Po_RHR, Strength == "Extreme")
# psych::describe(Po_eRHR$ACC)
# 
# Po_eRHR_RH <- filter(Po_eRHR, SLR == "Right Hands")
# psych::describe(Po_eRHR_RH$ACC)
# 
# Po_eRHR_LH <- filter(Po_eRHR, SLR == "Left Hands")
# psych::describe(Po_eRHR_LH$ACC)
# 
# Po_mRHR <- filter(Po_RHR, Strength == "Mixed")
# psych::describe(Po_mRHR$ACC)
# 
# Po_mRHR_RH <- filter(Po_mRHR, SLR == "Right Hands")
# psych::describe(Po_mRHR_RH$ACC)
# 
# Po_mRHR_LH <- filter(Po_mRHR, SLR == "Left Hands")
# psych::describe(Po_mRHR_LH$ACC)
# 
# Po_LHR <- filter(Po, Lat2 == "Lefty")
# psych::describe(Po_LHR$ACC)
# 
# Po_eLHR <- filter(Po_LHR, Strength == "Extreme")
# psych::describe(Po_eLHR$ACC)
# 
# Po_eLHR_RH <- filter(Po_eLHR, SLR == "Right Hands")
# psych::describe(Po_eLHR_RH$ACC)
# 
# Po_eLHR_LH <- filter(Po_eLHR, SLR == "Left Hands")
# psych::describe(Po_eLHR_LH$ACC)
# 
# Po_mLHR <- filter(Po_LHR, Strength == "Mixed")
# psych::describe(Po_mLHR$ACC)
# 
# Po_mLHR_RH <- filter(Po_mLHR, SLR == "Right Hands")
# psych::describe(Po_mLHR_RH$ACC)
# 
# Po_mLHR_LH <- filter(Po_mLHR, SLR == "Left Hands")
# psych::describe(Po_mLHR_LH$ACC)

```

```{r}
# Po_L_Finger <- filter(Po, version == "Response with Left Finger")
# psych::describe(Po_L_Finger$ACC)
# 
# Po_L_Finger_RH <- filter(Po_L_Finger, SLR == "Right Hands")
# psych::describe(Po_L_Finger_RH$ACC)
# 
# 
# Po_L_Finger_LH <- filter(Po_L_Finger, SLR == "Left Hands")
# psych::describe(Po_L_Finger_LH$ACC)
# 
# 
# Po_R_Finger <- filter(Po, version == "Response with Right Finger")
# 
# Po_R_Finger_RH <- filter(Po_R_Finger, SLR == "Right Hands")
# psych::describe(Po_R_Finger_RH$ACC)



# Po_R_Finger_LH <- filter(Po_R_Finger, SLR == "Left Hands")
# psych::describe(Po_R_Finger_LH$ACC)
# 

```

```{r}
# Po_mHR <- filter(Po, Strength == "Mixed")
# 
# Po_mHR_RH_Right_Finger <- filter(Po_mHR, SLR == "Right Hands",
#                                  version == "Response with Right Finger")
# psych::describe(Po_mHR_RH_Right_Finger$RT)
# 
# Po_mHR_LH_Right_Finger <- filter(Po_mHR, SLR == "Left Hands",
#                                  version == "Response with Right Finger")
# psych::describe(Po_mHR_LH_Right_Finger$RT)

```
# Descriptive for manuscript

```{r}
Mixed_LHR_LH <- Logfile %>% 
  filter(Lat2 == "Lefty",
         Strength == "Mixed",
         SLR == "Left Hands")
psych::describe(Mixed_LHR_LH$ACC)
psych::describe(Mixed_LHR_LH$RT)

```

```{r}
Mixed_LHR_RH <- Logfile %>% 
  filter(Lat2 == "Lefty",
         Strength == "Mixed",
         SLR == "Right Hands")
psych::describe(Mixed_LHR_RH$ACC)
psych::describe(Mixed_LHR_RH$RT)

```

```{r}
Extreme_LHR_LH <- Logfile %>% 
  filter(Lat2 == "Lefty",
         Strength == "Extreme",
         SLR == "Left Hands")
psych::describe(Extreme_LHR_LH$ACC)
psych::describe(Extreme_LHR_LH$RT)

```

```{r}
Extreme_LHR_RH <- Logfile %>% 
  filter(Lat2 == "Lefty",
         Strength == "Extreme",
         SLR == "Right Hands")
psych::describe(Extreme_LHR_RH$ACC)
psych::describe(Extreme_LHR_RH$RT)

```

```{r}
Mixed_RHR_LH <- Logfile %>% 
  filter(Lat2 == "Righty",
         Strength == "Mixed",
         SLR == "Left Hands")
psych::describe(Mixed_RHR_LH$ACC)
psych::describe(Mixed_RHR_LH$RT)

```

```{r}
Mixed_RHR_RH <- Logfile %>% 
  filter(Lat2 == "Righty",
         Strength == "Mixed",
         SLR == "Right Hands")
psych::describe(Mixed_RHR_RH$ACC)
psych::describe(Mixed_RHR_RH$RT)

```

```{r}
Extreme_RHR_LH <- Logfile %>% 
  filter(Lat2 == "Righty",
         Strength == "Extreme",
         SLR == "Left Hands")
psych::describe(Extreme_RHR_LH$ACC)
psych::describe(Extreme_RHR_LH$RT)

```

```{r}
Extreme_RHR_RH <- Logfile %>% 
  filter(Lat2 == "Righty",
         Strength == "Extreme",
         SLR == "Right Hands")
psych::describe(Extreme_RHR_RH$ACC)
psych::describe(Extreme_RHR_RH$RT)

```

** 2 way ANOVA for extreme handers **
ACC
```{r}
eHR <- filter(Logfile, Strength == "Extreme")

SLR_Lat2_acc_ex <- aov_car(ACC~SLR*Lat2+
            Error(subject/(SLR)),  data=eHR, anova_table = list(es = "pes"))     

knitr::kable(nice(SLR_Lat2_acc_ex)) ##call for formatted ANOVA table using knitr
```
```{r}

SLR_Lat2_RT_ex <- aov_car(RT~SLR*Lat2+
            Error(subject/(SLR)),  data=eHR, anova_table = list(es = "pes"))     

knitr::kable(nice(SLR_Lat2_RT_ex)) ##call for formatted ANOVA table using knitr
```

** t test for extreme lefty **
```{r}
Extreme_Lefty <- read_csv("~/Desktop/Handedness/Data_new/Step1/extreme_lefty.csv")

t_EL_acc <- t.test(Extreme_Lefty$L_ACC, Extreme_Lefty$R_ACC, paired = TRUE, var.equal = TRUE)
t_EL_acc

t_EL_rt <- t.test(Extreme_Lefty$L_RT, Extreme_Lefty$R_RT, paired = TRUE, var.equal = TRUE)
t_EL_rt
```

** t test for extreme righty **
```{r}
Extreme_Righty <- read_csv("~/Desktop/Handedness/Data_new/Step1/extreme_righty.csv")

t_ER_acc <- t.test(Extreme_Righty$L_ACC, Extreme_Righty$R_ACC, paired = TRUE, var.equal = TRUE)
t_ER_acc

t_ER_rt <- t.test(Extreme_Righty$L_RT, Extreme_Righty$R_RT, paired = TRUE, var.equal = TRUE)
t_ER_rt
```

** 2 way ANOVA for mixed handers **
```{r}
mHR <- filter(Logfile, Strength == "Mixed")

SLR_Lat2_acc_mixed <- aov_car(ACC~SLR*Lat2+
            Error(subject/(SLR)),  data=mHR, anova_table = list(es = "pes"))     

knitr::kable(nice(SLR_Lat2_acc_mixed)) ##call for formatted ANOVA table using knitr
```

```{r}
Lat2_SLR_acc_Interaction<-lsmeans(SLR_Lat2_acc_mixed, ~(Lat2*SLR))
Lat2_SLR_acc_Interaction

pairs(Lat2_SLR_acc_Interaction)

```

```{r}
SLR_Lat2_rt_mixed <- aov_car(RT~SLR*Lat2+
            Error(subject/(SLR)),  data=mHR, anova_table = list(es = "pes"))     

knitr::kable(nice(SLR_Lat2_rt_mixed)) ##call for formatted ANOVA table using knitr
```
```{r}
Lat2_SLR_rt_Interaction<-lsmeans(SLR_Lat2_rt_mixed, ~(Lat2*SLR))
Lat2_SLR_rt_Interaction

pairs(Lat2_SLR_rt_Interaction)

```

```{r}
mLHR_L <- filter(Logfile, Lat2 == "Lefty",
               Strength == "Mixed",
               SLR == "Left Hands")
psych::describe(mLHR_L$ACC)
psych::describe(mLHR_L$RT)


mLHR_R <- filter(Logfile, Lat2 == "Lefty",
               Strength == "Mixed",
               SLR == "Right Hands")
psych::describe(mLHR_R$ACC)
psych::describe(mLHR_R$RT)


```

** t test for mixed lefty **
```{r}
Mixed_Lefty <- read_csv("~/Desktop/Handedness/Data_new/Step1/Mixed_Lefty.csv")

t_ML_acc <- t.test(Mixed_Lefty$L_ACC, Mixed_Lefty$R_ACC, paired = TRUE, var.equal = TRUE)
t_ML_acc

t_ML_rt <- t.test(Mixed_Lefty$L_RT, Mixed_Lefty$R_RT, paired = TRUE, var.equal = TRUE)
t_ML_rt
```

** t test for mixed righty **

```{r}
Mixed_Righty <- read_csv("~/Desktop/Handedness/Data_new/Step1/Mixed_Righty.csv")

t_MR <- t.test(Mixed_Righty$L_ACC, Mixed_Righty$R_ACC, paired = TRUE, var.equal = TRUE)
t_MR

t_MR_rt <- t.test(Mixed_Righty$L_RT, Mixed_Righty$R_RT, paired = TRUE, var.equal = TRUE)
t_MR_rt
```
** mixed left hander left hand vs. mixed right hander left hand **
```{r}
t.test(Mixed_Lefty$L_ACC, Mixed_Righty$L_ACC, paired = FALSE, var.equal = TRUE)

t.test(Mixed_Lefty$L_RT, Mixed_Righty$L_RT, paired = FALSE, var.equal = TRUE)
```

** mixed left hander left hand vs. mixed right hander right hand **
```{r}
t.test(Mixed_Lefty$L_ACC, Mixed_Righty$R_ACC, paired = FALSE, var.equal = TRUE)

t.test(Mixed_Lefty$L_RT, Mixed_Righty$R_RT, paired = FALSE, var.equal = TRUE)
```

** mixed left hander right hand vs. mixed right hander right hand **
```{r}
t.test(Mixed_Lefty$R_ACC, Mixed_Righty$R_ACC, paired = FALSE, var.equal = TRUE)

t.test(Mixed_Lefty$R_RT, Mixed_Righty$R_RT, paired = FALSE, var.equal = TRUE)
```

** mixed left hander right hand vs. mixed right hander left hand **
```{r}
t.test(Mixed_Lefty$R_ACC, Mixed_Righty$L_ACC, paired = FALSE, var.equal = TRUE)

t.test(Mixed_Lefty$R_RT, Mixed_Righty$L_RT, paired = FALSE, var.equal = TRUE)
```
**Initial 2 way ANOVA**
```{r}
SLR_Lat2_acc <- aov_car(ACC~SLR*Lat2+
            Error(subject/(SLR)),  data=Logfile, anova_table = list(es = "pes"))     

knitr::kable(nice(SLR_Lat2_acc)) ##call for formatted ANOVA table using knitr
```

**ACC**


```{r}
SLR_Lat2_Strength_acc <- aov_car(ACC~SLR*Lat2*Strength+
            Error(subject/(SLR)),  data=Logfile, anova_table = list(es = "pes"))     

knitr::kable(nice(SLR_Lat2_Strength_acc)) ##call for formatted ANOVA table using knitr
```

```{r}
Lat2_Strength_acc_Interaction<-lsmeans(SLR_Lat2_Strength_acc, ~(Lat2*Strength))
Lat2_Strength_acc_Interaction
```

```{r}
pairs(Lat2_Strength_acc_Interaction)
```

```{r}
contrast(Lat2_Strength_acc_Interaction, alpha=0.05, method="pairwise", adjust="Tukey")
```

```{r}
SLR_Lat2_Strength_acc_Interaction<-lsmeans(SLR_Lat2_Strength_acc, ~SLR|(Lat2*Strength))
SLR_Lat2_Strength_acc_Interaction
```

```{r}
pairs(SLR_Lat2_Strength_acc_Interaction)
```
```{r}
contrast(SLR_Lat2_Strength_acc_Interaction, alpha=0.05, method="pairwise", adjust="Tukey")
```


```{r}
update(pairs(SLR_Lat2_Strength_acc_Interaction, by = "SLR"), by = NULL)
```
** Gesture Type **

```{r}
# SLR_Lat2_Strength_acc <- aov_car(ACC~SLR*Lat2*Strength*GestureType+
#             Error(subject/(SLR*GestureType)),  data=Logfile, anova_table = list(es = "pes"))     
# 
# knitr::kable(nice(SLR_Lat2_Strength_acc)) ##call for formatted ANOVA table using knitr
```

```{r}
# Lat2_Strength_acc_Interaction<-lsmeans(SLR_Lat2_Strength_acc, ~(Lat2*Strength))
# Lat2_Strength_acc_Interaction
```

```{r}
# pairs(Lat2_Strength_acc_Interaction)
```

```{r}
# acc_Interaction2 <-lsmeans(SLR_Lat2_Strength_acc, ~SLR|(Lat2*Strength))
# acc_Interaction2
```

```{r}
# pairs(acc_Interaction2)
```

```{r}
# update(pairs(acc_Interaction2, by = "SLR"), by = NULL)
```


```{r}
# acc_Interaction3 <-lsmeans(SLR_Lat2_Strength_acc, ~(Lat2*Strength*GestureType))
# acc_Interaction3
```

```{r}
# pairs(acc_Interaction3)
```

```{r}
# ELL
ELL <- filter(Logfile, Lat2 == "Lefty") %>% 
  filter(Strength == "Extreme") %>% filter(SLR == "Left Hands")

Ex_LL <- ELL %>% 
  summarize(
    mean_ELL_ACC = mean(ACC),
    se_ELL_ACC = sd(ACC)/sqrt(nrow(ELL)),
    mean_ELL_RT = mean(RT),
    se_ELL_RT = sd(RT)/sqrt(nrow(ELL))
  )

# ELR
ELR <- filter(Logfile, Lat2 == "Lefty") %>% 
  filter(Strength == "Extreme") %>% filter(SLR == "Right Hands")

Ex_LR <- ELR %>% 
  summarize(
    mean_ELR_ACC = mean(ACC),
    se_ELR_ACC = sd(ACC)/sqrt(nrow(ELR)),
    mean_ELR_RT = mean(RT),
    se_ELR_RT = sd(RT)/sqrt(nrow(ELR))
  )


# MLL
MLL <- filter(Logfile, Lat2 == "Lefty") %>% 
  filter(Strength == "Mixed") %>% filter(SLR == "Left Hands")
Mixed_LL <- MLL %>% 
  summarize(
    mean_MLL_ACC = mean(ACC),
    se_MLL_ACC = sd(ACC)/sqrt(nrow(MLL)),
    mean_MLL_RT = mean(RT),
    se_MLL_RT = sd(RT)/sqrt(nrow(MLL))
  )

# MLR
MLR <- filter(Logfile, Lat2 == "Lefty") %>% 
  filter(Strength == "Mixed") %>% filter(SLR == "Right Hands")
Mixed_LR <- MLR %>% 
  summarize(
    mean_MLR_ACC = mean(ACC),
    se_MLR_ACC = sd(ACC)/sqrt(nrow(MLR)),
    mean_MLR_RT = mean(RT),
    se_MLR_RT = sd(RT)/sqrt(nrow(MLR))
  )

# MRL
MRL <- filter(Logfile, Lat2 == "Righty") %>% 
  filter(Strength == "Mixed") %>% filter(SLR == "Left Hands")
Mixed_RL <- MRL %>% 
  summarize(
    mean_MRL_ACC = mean(ACC),
    se_MRL_ACC = sd(ACC)/sqrt(nrow(MRL)),
    mean_MRL_RT = mean(RT),
    se_MRL_RT = sd(RT)/sqrt(nrow(MRL))
  )

# MRR
MRR <- filter(Logfile, Lat2 == "Righty") %>% 
  filter(Strength == "Mixed") %>% filter(SLR == "Right Hands")
Mixed_RR <- MRR %>% 
  summarize(
    mean_MRR_ACC = mean(ACC),
    se_MRR_ACC = sd(ACC)/sqrt(nrow(MRR)),
    mean_MRR_RT = mean(RT),
    se_MRR_RT = sd(RT)/sqrt(nrow(MRR))
  )

# ERL
ERL <- filter(Logfile, Lat2 == "Righty") %>% 
  filter(Strength == "Extreme") %>% filter(SLR == "Left Hands")
Ex_RL <- ERL %>% 
  summarize(
    mean_ERL_ACC = mean(ACC),
    se_ERL_ACC = sd(ACC)/sqrt(nrow(ERL)),
    mean_ERL_RT = mean(RT),
    se_ERL_RT = sd(RT)/sqrt(nrow(ERL))
  )

# ERR
ERR <- filter(Logfile, Lat2 == "Righty") %>% 
  filter(Strength == "Extreme") %>% filter(SLR == "Right Hands")
Ex_RR <- ERR %>% 
  summarize(
    mean_ERR_ACC = mean(ACC),
    se_ERR_ACC = sd(ACC)/sqrt(nrow(ERR)),
    mean_ERR_RT = mean(RT),
    se_ERR_RT = sd(RT)/sqrt(nrow(ERR))
  )

```


```{r}

# LT <- filter(Logfile, Lat2 == "Lefty")
# levels(LT$Strength)[levels(LT$Strength)=="Mixed"] <- "Mixed Left-hander"
# levels(LT$Strength)[levels(LT$Strength)=="Extreme"] <- "Extreme Left-hander"
# 
# RT <- filter(Logfile, Lat2 == "Righty")
# levels(RT$Strength)[levels(RT$Strength)=="Mixed"] <- "Mixed Right-hander"
# levels(RT$Strength)[levels(RT$Strength)=="Extreme"] <- "Extreme Right-hander"
# 
# pd <- position_dodge(0.1) # move them .05 to the left and right
# p_LT <-ggplot(data = LT,aes(x = Strength, color = as.factor(SLR), group = SLR, y = ACC)) +
#   stat_summary(fun.y = mean, geom = "point", size =5, shape=21, fill="white") +
#   stat_summary(fun.y = mean, geom = "line", size = 1.2) +
#   stat_summary(fun.data = "mean_se", geom="errorbar", width = .5, position = pd) +
#   scale_x_discrete(limits = c("Extreme Left-hander", "Mixed Left-hander"), labels = function(labels){
#     fixedLabels <- c()
#     for (l in 1:length(labels)){
#       fixedLabels[l] <-paste0(ifelse(l %% 2 == 0, '', '\n'), labels[l])
#     }
#     return(fixedLabels)
#   })+
#   scale_y_continuous(breaks = seq(0, 1, by=0.1), limits=c(0,1))+
#   labs(x= "Strength", y="ACC", color="", fill="Hand-tested")  + theme_classic() +     
#   theme(text=element_text(face="bold", size=20), legend.position = "none", axis.title.x=element_blank())
# 
# p_ACC <-ggplot(data = RT,aes(x = Strength, color = as.factor(SLR), group = SLR, y = ACC)) +
#   stat_summary(fun.y = mean, geom = "point", size =5, shape=21, fill="white") +
#   stat_summary(fun.y = mean, geom = "line", size = 1.2) +
#     scale_x_discrete(labels = function(labels){
#     fixedLabels <- c()
#     for (l in 1:length(labels)){
#       fixedLabels[l] <-paste0(ifelse((l+1) %% 2 == 0, '', '\n'), labels[l])
#     }
#     return(fixedLabels)
#   })+
#   stat_summary(fun.data = "mean_se", geom="errorbar", width = .5, position = pd) +
#   scale_y_continuous(breaks = seq(0, 1, by=0.1), limits=c(0,1), position = "right", alpha(1))+
#   labs(color="", fill="Hand-tested")  + theme_classic() +     
#   theme(text=element_text(face="bold", size=20), axis.title.y=element_blank(), axis.text.y=element_blank(),
#   axis.title.x=element_blank())+ annotate("text", x = 1, y = 0.97, label = "*", color = "black", size = 16)


# Figure5a <- ggarrange(p_LT, p_RT, widths = c(0.8, 1),
#                 ncol = 2, nrow = 1)
# 
# #Figure5a_ud <- annotate_figure(Figure5a, bottom = text_grob("Strength", color = "black", face = "bold", size = 23, fig.lab.pos = "bottom"))
# Figure5a
# 
# ggsave("5a.png", width = 10, height = 6)
```

**ACC VERSION**

```{r}
SLR_Lat2_Strength_version_acc <- aov_car(ACC~SLR*Lat2*Strength*version+
            Error(subject/(SLR)),  data=Logfile, anova_table = list(es = "pes"))     

knitr::kable(nice(SLR_Lat2_Strength_version_acc)) ##call for formatted ANOVA table using knitr
```
```{r}
SLR_Lat2_Strength_Interaction<-lsmeans(SLR_Lat2_Strength_version_acc, ~(Lat2*Strength))
SLR_Lat2_Strength_Interaction
```

```{r}
pairs(SLR_Lat2_Strength_Interaction)
```

```{r}
SLR_version_Interaction<-lsmeans(SLR_Lat2_Strength_version_acc, ~(SLR|version))
SLR_version_Interaction
```

```{r}
pairs(SLR_version_Interaction)
```

```{r}
update(pairs(SLR_version_Interaction, by = "SLR"), by = NULL)
```

```{r}
SLR_Lat2_Strength_Interaction<-lsmeans(SLR_Lat2_Strength_version_acc, ~SLR|(Lat2*Strength))
SLR_Lat2_Strength_Interaction
```

```{r}
pairs(SLR_Lat2_Strength_Interaction)
```

```{r}
update(pairs(SLR_Lat2_Strength_Interaction, by = "SLR"), by = NULL)
```


```{r}
SLR_Lat2_Strength_version_acc_Interaction<-lsmeans(SLR_Lat2_Strength_version_acc, ~SLR|(version*Strength))
SLR_Lat2_Strength_version_acc_Interaction
```

```{r}
pairs(SLR_Lat2_Strength_version_acc_Interaction)
```

```{r}
update(pairs(SLR_Lat2_Strength_version_acc_Interaction, by = "SLR"), by = NULL)
```


** strategy **

```{r}
STR <- filter(Logfile, Strategy == "Mental Rotation"|Strategy == "Thumb Strategy")
```

```{r}
SLR_Lat2_Strength_Strategy_acc <- aov_car(ACC~SLR*Lat2*Strength*Strategy+
            Error(subject/(SLR)),  data=STR, anova_table = list(es = "pes"))     

knitr::kable(nice(SLR_Lat2_Strength_Strategy_acc)) ##call for formatted ANOVA table using knitr
```
```{r}
SLR_Lat2_Strength_Strateg_Interaction<-lsmeans(SLR_Lat2_Strength_Strategy_acc, ~(SLR|Lat2*Strength*Strategy))
SLR_Lat2_Strength_Strateg_Interaction
```

```{r}
pairs(SLR_Lat2_Strength_Strateg_Interaction)
```
